DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
improved illustrative example
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> system = tf(num,den,0.002);
>> y = synthesize(system,8,8,1,-1);
>> SYNTHESIS SUCCESSFUL
>> y = 
>>  -0.9983 z^2 + 0.09587 z + 0.1926
>>  --------------------------------
>>       z^2 + 0.5665 z + 0.75
\end{lstlisting}
\vspace{-0.2cm}
\caption{Synthesis of a digital controller for the physical plant defined in Eq.(\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
\label{toolbox-usage}
\end{figure}

@@

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.99832 0.09587 0.1926];
>> den = [1 0.5665 0.75];
>> controller = tf(num,den,0.002);
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> plant = tf(num,den,0.002);
>> sys = series(controller,plant)
>> sys =
>> 
>>      0.06863 z^4 - 0.006591 z^3 - 0.01324 z^2
>>  ------------------------------------------------
>>  z^4 - 1.129 z^3 + 0.4981 z^2 - 0.8704 z + 0.5317
\end{lstlisting}
\vspace{-0.2cm}
\caption{General equation for the closed-loop control system using the series configuration (as shown in Fig.~\ref{fig:typical-control-system}).}
\label{combine-controller-plant}
\end{figure}

The general equation that represents the closed-loop control system using the series 
configuration is described by Equation~\ref{equation_general} as follows
%
\begin{equation}
\small
\label{equation_general}
\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{z^{4} - 1.129z^{3} + 0.4981z^{2} -0.8704z + 0.5317}.
\end{equation}

@@

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> den = [1 -1.129 0.4981 -0.8704 0.5317]
>> r = roots(den)
>> r =
>>  -0.2833 + 0.8185i
>>  -0.2833 - 0.8185i
>>   0.9480 + 0.0000i
>>   0.7476 + 0.0000i
\end{lstlisting}
\vspace{-0.2cm}
\caption{Roots of the polynomial $D(z)$ given by Equation~\ref{equation_general}.}
\label{roots-of-dz}
\end{figure}

>>>>

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> system = tf(num,den,0.002);
>> y = synthesize(system,8,8,1,-1);
>> SYNTHESIS SUCCESSFUL
>> y = 
>>  -0.9983z^2 + 0.09587z + 0.1926
>>  --------------------------------
>>       z^2 + 0.5665z + 0.75
\end{lstlisting}
\vspace{-0.2cm}
\caption{Synthesis of a digital controller for the physical plant defined in Eq.(\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
\label{toolbox-usage}
\end{figure}

@@

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.99832 0.09587 0.1926];
>> den = [1 0.5665 0.75];
>> controller = tf(num,den,0.002);
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> plant = tf(num,den,0.002);
>> sys = feedback(series(controller, plant),1)
>> sys =
>>        0.06863z^4 - 0.006591z^3 - 0.01324z^2
>> ---------------------------------------------------
>> 1.069z^4 - 1.136z^3 + 0.4849z^2 - 0.8704z + 0.5317
\end{lstlisting}
\vspace{-0.2cm}
\caption{General equation for the closed-loop control system.}
\label{combine-controller-plant}
\end{figure}

The general equation that represents the closed-loop control system 
is described by Equation~\ref{equation_general} as follows
%
\begin{equation}
\small
\label{equation_general}
\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{1.069z^{4} - 1.136z^{3} + 0.4849z^{2} -0.8704z + 0.5317}.
\end{equation}

@@

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> den = [1.069 -1.136 0.4849 -0.8704 0.5317]
>> r = roots(den)
>> r =
>>  -0.2912 + 0.8061i
>>  -0.2912 - 0.8061i
>>   0.8225 + 0.0219i
>>   0.8225 - 0.0219i
\end{lstlisting}
\vspace{-0.2cm}
\caption{Roots of the polynomial $D(z)$ given by Equation~\ref{equation_general}.}
\label{roots-of-dz}
\end{figure}
